\textbf{Discovery of a disrupting open cluster in the Galactic halo:\\ a recent star formation event in the leading arm of the Magellanic stream}

### 2018-11-03 ms.tex
names

% Notebook: Figure-DECam-CMD
\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/DECam-cmd.pdf}
\caption{\decam\ $g-i$ versus $g$ color-magnitude diagrams for the \decam\ control fields (left panel) and \decam\ cluster fields (right panel).
Note the prominent young, distant main sequence in the cluster fields: This is the main sequence of \clustername.
The sources in the dashed (red) rectangle in the right panel are later used to measure the cluster stellar population parameters.
}
\label{fig:decam-cmd}
\end{figure}

@@

\subsection{Measuring the mean proper motion of \clustername}
\label{sec:pmclean}

@@

\subsection{Stellar population modeling}
\label{sec:popmodel}

@@

\todo{we ignore the $q$!}
With the marginal likelihood (\equationname~\ref{eq:marglike}), we then need to specify prior probability distributions for the hyperparameters $(\bs{\alpha}, f)$, and we can then generate posterior samples for the hyperparameters;
We use uniform priors for all of these, as summarized in \tablename~\ref{tbl:hyperpriors}.
We then use \texttt{emcee} \citep{Goodman:2010, Foreman-Mackey:2013} to sample from the posterior probability distribution for the hyperparameters given all of the photometric data,
\begin{equation}
    p(\bs{\alpha}, f \given \{\bs{m}_k\}) \propto
        p(\bs{\alpha}) \, p(f) \,
        \prod_k^K p(\bs{m}_k \given \bs{\alpha}, f) \quad .
\end{equation}
Here we use 64 walkers and run for an initial 128 steps to burn-in the sampler before running for a final 1024 steps.
\figurename~\ref{fig:hierarch-corner} shows a corner plot showing all 1D and 2D marginal posterior probability distributions estimated from the samples.

>>>>

% Notebook: Figure-DECam-CMD
\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{figures/DECam-cmd.pdf}
\caption{\decam\ $g-i$ versus $g$ color-magnitude diagrams for the \decam\ control fields (left panel) and \decam\ cluster fields (right panel).
Note the prominent young, distant main sequence in the cluster fields: This is the main sequence of \clustername.
The sources in the dashed (red) rectangle in the right panel are later used to measure the cluster stellar population parameters.
}
\label{fig:decam-cmd}
\end{figure}

@@

\subsection{Inferring the mean proper motion}
\label{sec:pmclean}

@@

\subsection{Inferring the stellar population parameters}
\label{sec:popmodel}

@@

\todo{we ignore the $q$!}
With the marginal likelihood (\equationname~\ref{eq:marglike}), we then need to specify prior probability distributions for the hyperparameters $(\bs{\alpha}, f)$, and we can then generate posterior samples for the hyperparameters;
We use uniform priors for all of these, as summarized in \tablename~\ref{tbl:hyperpriors}.
We then use \texttt{emcee} \citep{Goodman:2010, emcee} to sample from the posterior probability distribution for the hyperparameters given all of the photometric data,
\begin{equation}
    p(\bs{\alpha}, f \given \{\bs{m}_k\}) \propto
        p(\bs{\alpha}) \, p(f) \,
        \prod_k^K p(\bs{m}_k \given \bs{\alpha}, f) \quad .
\end{equation}
Here we use 64 walkers and run for an initial 128 steps to burn-in the sampler before running for a final 1024 steps.
\figurename~\ref{fig:hierarch-corner} shows a corner plot showing all 1D and 2D marginal posterior probability distributions estimated from the samples.
